A Fredholm operator approach to the plate buckling problem

### 2018-07-12 doc/draft-01/01intro.tex

While integral equation methods for the buckling problem
have been considered previously, the existing formulations
have resulted in first kind integral equations, i.e. equations
in which the operator is compact \cite{kitahara2014boundary,
  antunes2011buckling}. This is unsatisfying from a theoretical
perspective, because such operators are never invertible
(though, they are injective precisely when $k^2$ is an
eigenvalue \cite{kitahara2014boundary}) so that the
relation between the non-invertibility of the discrete system
and the eigenvalues is obscured. Further, such representations
create numerical challenges because common measures of the
``non-invertibility'' of a matrix, like the smallest singular
value or the determinant, converge rapidly to zero for all
values of $k^2$ as the boundary is refined.

Second kind integral equations, i.e. integral equations
of the form $\mathcal{I} + \mathcal{K}$ where $\mathcal{K}$
is compact, have a more satisfying theory
\cite{reed1972methods}, which translates
well to numerical implementation
\cite{bornemann2010numerical,zhao2015robust}.
In \cite{zhao2015robust}, Zhao and Barnett demonstrated
that the eigenvalues of the drum problem can be
computed with such a framework, resulting in
spectrally accurate numerical methods.
In this paper, we develop a second kind integral
equation for the buckling problem, based on the
approach in \cite{rachh2017integral}. This allows
for a robust approach to computing the eigenvalues
of the buckling problem, model after the approach for
the drum problem in \cite{zhao2015robust}, which we
demonstrate with a number of examples.

>>>>

While integral equation methods for the buckling problem
have been considered previously, the existing formulations
have resulted in first kind integral equations, i.e. equations
in which the operator is compact \cite{kitahara2014boundary,
  antunes2011buckling}. This is unsatisfying from a theoretical
perspective, because such operators are never invertible
(though, they are injective precisely when $k^2$ is an
eigenvalue \cite{kitahara2014boundary}) so that the
relation between the non-invertibility of the discrete system
and the eigenvalues is obscured. Further, such representations
create numerical challenges because common measures of the
``non-invertibility'' of a matrix, like the smallest singular
value or the determinant, converge rapidly to zero for all
values of $k^2$ as the boundary is refined. Therefore, the
measure of whether $k^2$ is an approximate eigenvalue is
{\em relative to the current grid} for first kind equations.

Second kind integral equations, i.e. integral equations
of the form $\mathcal{I} + \mathcal{K}$ where $\mathcal{K}$
is compact, have a more satisfying theory
\cite{reed1972methods,kress1989linear},
which translates well to numerical implementation
\cite{atkinson2009numerical,bornemann2010numerical,
  hackbusch2012integral,zhao2015robust}. Two facts are
of particular importance here: with an appropriately
chosen representation, (a) the Fredholm determinant of the
integral equation will be a well-defined analytic function
of $k^2$ with zeros precisely at the eigenvalues and (b) the 
determinant of the matrix resulting from
a Nystr\"{o}m discretization of the integral equation
will converge to the Fredholm determinant of the operator
\cite{bornemann2010numerical}.
In \cite{zhao2015robust}, Zhao and Barnett demonstrated
that the eigenvalues of the drum problem can be
computed with such a framework, resulting in
methods which are spectrally accurate with respect
to both the sampling of the boundary and the sampling
in $k^2$. There are natural extensions of existing second
kind integral
equations for the biharmonic \cite{farkas1989mathematical}
and modified biharmonic \cite{jiang2013second} equations
which would be appropriate for the buckling problem, but
these representations suffer from instability for
high curvature domains, limiting their applicability
\cite{rachh2017integral}.
In this paper, we develop a second kind integral
equation for the buckling problem based on Stokeslet
and stresslet inspired kernels, as was done for the
$k=0$ case in \cite{rachh2017integral}. This allows
for a robust approach to computing the eigenvalues
of the buckling problem, modeled after the approach for
the drum problem in \cite{zhao2015robust}, which we
demonstrate with a number of examples from the
literature.
